Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-03-06 ms.tex
Typesetting fixes
Removed double-spaces between sentences
Added the all-important footnote

Ground-based gravitational-wave interferometers are entering the advanced detector era, positioning themselves to make profound discoveries about the universe.  The advanced LIGO and Vigo detectors will be part of a worldwide network that also includes KAGRA and hopefully LIGO-India.  Coalescing neutron star binaries are among the most likely sources, with event rates of $~ 50/\mathrm{yr}$ (check that number!).  In addition to being an efficient source of gravitational waves, the neutron star may be tidally shredded before merging, providing fuel for an electromagnetic counterpart.  The short-lived accretion flow may power a collimated relativistic jet, resulting in a short gamma-ray burst and an X-ray afterglow if it is aligned with the line of sight. An optical afterglow may follow minutes to hours later as the jet plows into the interstellar medium. As surrounding neutron-rich ejecta decay radioactively, an optical 'kilonova' may be visible after ~1 day. Finally, as the ejecta plow into the interstellar medium, a faint radio afterglow will occur on a timescale of years.

@@

>>>>

Ground-based gravitational-wave interferometers are entering the advanced detector era, positioning themselves to make profound discoveries about the universe. The advanced LIGO and Vigo detectors will be part of a worldwide network that also includes KAGRA and hopefully LIGO-India. Coalescing neutron star binaries are among the most likely sources, with event rates of $~ 50/\mathrm{yr}$ (check that number!). In addition to being an efficient source of gravitational waves, the neutron star may be tidally shredded before merging, providing fuel for an electromagnetic counterpart. The short-lived accretion flow may power a collimated relativistic jet, resulting in a short gamma-ray burst and an X-ray afterglow if it is aligned with the line of sight. An optical afterglow may follow minutes to hours later as the jet plows into the interstellar medium. As surrounding neutron-rich ejecta decay radioactively, an optical `kilonova' may be visible after $~$1 day. Finally, as the ejecta plow into the interstellar medium, a faint radio afterglow will occur on a timescale of years.

@@

We have developed a rapid-response sky localization algorithm called \ac{BAYESTAR}%
%
\footnote{A pun on the Cylon battleships in the American television series Battlestar Galactica. The defining characteristic of the Cylons is that they repeatedly defeat humanity by using their superhuman information\nobreakdashes-gathering ability to coordinate overwhelming forces. The name also suggests that, like the Cylons, gravitational-wave detectors may some day rise against us humans.}%
%
\footnote{We do not like to mention the final `T' in the acronym, because then it would be called BAYES\nobreakdashes-TART, which would sound ridiculous.}%
